{\LARGE Basis Choice for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-08 Paper/main.tex

	\subsection{Application - Coefficient Function Estimates}
	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/appl\_basis\_expansion.pdf}
			\caption{Basis Expansion Regression}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm2.pdf}
			\caption{2 Functional Principal Components}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm3.pdf}
			\caption{3 Functional Principal Components}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr_nharm4.pdf}
			\caption{4 Functional Principal Components}
		\end{minipage}
	\end{figure}

>>>>

	\subsection{Application - Coefficient Function Estimates}
	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/appl\_basis\_expansion.pdf}
			\caption{Basis Expansion Regression}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm2.pdf}
			\caption{2 Functional Principal Components}
		\end{minipage}
	\end{figure}

	\begin{figure}[H]
		\centering
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm3.pdf}
			\caption{3 Functional Principal Components}
		\end{minipage}%
		\begin{minipage}{.5\textwidth}
			\centering
			\includegraphics[width=\textwidth]{../Graphics/Appl\_Curve\_Estimates/fpcr\_nharm4.pdf}
			\caption{4 Functional Principal Components}
		\end{minipage}
	\end{figure}
